A Constraint Solving Approach to Parikh Images of Regular Languages

### 2023-07-11 calculus.tex

A proof in which all proof goals could be closed shows that the formulas
in the root~$\SomeClause$ of the proof are inconsistent and do not
have any solutions. A proof goal that could not be closed but to which no
more rules are applicable gives rise to a solution of the formulas in the
root~$\SomeClause$. Such an open proof goal will only contain formulas
in Presburger arithmetic, allowing a solution to be computed using
standard algorithms~\cite{Fitting96a}.

>>>>

A proof in which all proof goals are closed witnesses that the formulas
in the root~$\SomeClause$ of the proof are inconsistent, and do not
have any solutions. A proof goal that cannot be closed, but to which no
more rules are applicable, gives rise to  a solution of the formulas in the
root~$\SomeClause$. Such an open proof goal will only contain formulas
in Presburger arithmetic allowing a solution to be computed using
standard algorithms~\cite{DBLP:books/daglib/0022394}.
